InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-22 paper.tex
Make use of provided command to separate author names

\author{Max Buchholz, Lukas Müller, Levi Otterbach \& Raphael Weber}

@@

@@

The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2 \cite{solaiman2019release}. It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 billion parameters. The RoBERTa Base OpenAI Detector can be used to classify texts, on whether they are likely to be created by the GPT-2 model. It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released. The model is limited to english texts only and is openly available under the MIT license.

>>>>

\author{Max Buchholz \And Lukas Müller \And Levi Otterbach \And Raphael Weber}

@@

The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2. It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 Billion parameters. The RoBERTa Base OpenAI Detector can be used to classify texts, on whether they are likely to be created by the GPT-2 model. It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.

@@
